---
title: "Renal Disease Take Home Project Answers"
author: "Jonathan Pedroza, JP"
date: "10/20/2021"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

getwd()

library(tidyverse)
```

## Mentor Milestone 1 (students usually cover this during week 1 + 2)

Import the project data and recreate the ggplot below. Then, extend the milestone by creating another plot to demonstrate your understanding of ggplot.

Step 1: Read in `baseline_data.xpt` (MDRD data) and recreate the plot below.

```{r loading in baseline data}
baseline <- haven::read_xpt(here::here("take_home_to_be_completed", "data/baseline_data.xpt"))

# baseline <- haven::read_xpt("../data/baseline_data.xpt")
```

Recreate the plot in this chunk:

```{r milestone-1-recreation}
ggplot(data = baseline, aes(gfr)) + 
  geom_histogram()
```

Step 2: Create a second plot below:

```{r milestone-1-extension}

baseline %>% 
  pivot_longer(cols = c("gfr", "followup"), names_to = "before_after", values_to = "gfr_values") %>% 
  mutate(before_after = factor(before_after),
         dropout = factor(dropout),
         before_after = relevel(before_after, ref = "gfr"),
         dropout = recode(dropout,
                          "0" = "Continued",
                          "1" = "Dropped Out"),
         before_after = recode(before_after,
                               "gfr" = "Baseline GFR",
                               "followup" = "Followup GFR")) %>% 
  group_by(dropout, before_after) %>% 
  mutate(avg_gfr = mean(gfr_values)) %>% 
  ungroup() %>% 
  ggplot(aes(before_after, avg_gfr, group = dropout)) + 
  geom_line(aes(color = dropout), size = 1.25) + 
    geom_point(aes(color = dropout), size = 1.25) +
  labs(title = "Change in Average GFR At Baseline and Follow-up",
       subtitle = "For Patients that Continued or Dropped Out",
       x = "",
       y = "GFR Value",
       caption = "GFR = Glomerular Filtration Rate") + 
  scale_color_manual(values = c("#387448", "#d74122")) + 
  theme_minimal() +
  theme(legend.title = element_blank())
  
```

## Mentor Milestone 2

Read in the data from data/baseline_data.xpt and data/data_supplemental.xlsx
data_dictionary.md in the data folder explains the variables in both data sets (in case you’d like to learn more about the data)
The formula for BMI is kilograms / meters^2
Please do and save your work below:

For your extension, please demonstrate your understanding of summarizing data sets.

```{r milestone-2-recreation}
supplemental <- readxl::read_xlsx(here::here("take_home_to_be_completed", "data/data_supplemental.xlsx"))

data <- left_join(baseline, supplemental, by = "ptid")

data <- data %>% 
  mutate(bmi = weight/height^2)

data %>% 
  select(ptid, gfr, age, bmi) %>% 
  print()
```

---------------------------------------------------

```{r milestone-2-extension}
data %>% 
  summarize(avg_bmi = mean(bmi, na.rm = TRUE),
            med_bmi = median(bmi),
            variance = sd(bmi)^2,
            sd_bmi = sd(bmi),
            n = n())

data %>% 
  mutate(dietl_n = recode(dietl_n, "1" = "Yes",
                          "0" = "No")) %>% 
  group_by(sex, dietl_n) %>% 
  summarize(avg_bmi = mean(bmi, na.rm = TRUE),
            med_bmi = median(bmi),
            variance = sd(bmi)^2,
            sd_bmi = sd(bmi),
            n = n())

data %>% 
  filter(dropout == 0) %>% 
  summarize(avg_bmi = mean(bmi, na.rm = TRUE),
            med_bmi = median(bmi),
            variance = sd(bmi)^2,
            sd_bmi = sd(bmi),
            n = n())

data %>% 
  group_by(dietl_n, dietk_n) %>% 
  filter(dietl_n == 1 |
           dietk_n == 1) %>% 
  summarize(avg_bmi = mean(bmi, na.rm = TRUE),
            med_bmi = median(bmi),
            variance = sd(bmi)^2,
            sd_bmi = sd(bmi),
            n = n())

data %>% 
  pivot_longer(cols = c("dietl_n", "dietl_l", "dietk_n", "dietk_l"), names_to = "diet_assignment", values_to = "diet_values") %>% 
  filter(diet_assignment == "dietl_n") %>% 
  summarize(avg_bmi = mean(bmi, na.rm = TRUE),
            med_bmi = median(bmi),
            variance = sd(bmi)^2,
            sd_bmi = sd(bmi),
            n = n())
```

## Mentor Milestone 3 (students usually cover this during week 9)

This milestone is about iteration with `purrr`. Your objective is to use iteration to load in the 100 files found in the `/data/milestone-3` directory.

Please do and save your work below:

```{r milestone-3-recreation, warning = FALSE, message = FALSE}

data_files <- fs::dir_ls(here::here("take_home_to_be_completed/data", "milestone-3"),
                         glob = "*.csv")

data_combined <-map_dfr(data_files, read_csv)

```

```{r}
head(data_combined, 10)
```


For your milestone extension, please choose from the following 2 options:

-  Explain the difference between `map()` and its variants, such as `map_chr()`.

**Answer**: The difference between `map()` and its variants is that `map()` will always return a list, while the variants will return the appropriate vector depending on the variant function. For instance, `map_chr()` will return a character vector if working with strings.

-  Share an example of how you've used `purrr` in the past.





