---
title: "formula_one"
author: "JP"
date: "12/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = FALSE}
library(tidyverse)
cat_map <- purrr::map
library(maps)
library(maptools)
library(ggmap)
library(tidymodels)

options(scipen = 999)
theme_set(theme_light())
```

```{r include data, echo = FALSE, eval = TRUE}
d1 <- read_csv("tidy_tuesday/f1_data1.csv")
d2 <- read_csv("tidy_tuesday/f1_data2.csv")

d2 <- d2 %>% 
  mutate(constructor_season_pos_text = as.character(constructor_season_pos_text),
         gp_start_time = as.character(gp_start_time),
         q1 = as.character(q1),
         q2 = as.character(q2),
         final_driver_pos = as.character(final_driver_pos),
         final_driver_pos_text = as.character(final_driver_pos_text),
         fastest_lap = as.character(fastest_lap),
         fast_lap_rank = as.character(fast_lap_rank),
         fastest_lap_time = as.character(fastest_lap_time),
         fastest_lap_speed = as.character(fastest_lap_speed))

# glimpse(d1)
# glimpse(d2)

data <- bind_rows(d1, d2)

f1 <- data %>% 
  mutate(engine_disp = case_when(year >= 2000 & year <= 2005 ~ "V10",
                                 year >= 2006 & year <= 2008 ~ "V8",
                                 year >= 2009 & year <= 2013 ~ "V8 KERS",
                                 year >= 2014 ~ "V6"),
         engine_disp = as.factor(engine_disp)) %>% 
  filter(year >= 2000) %>% 
  rename(num_fastest_lap = fastest_lap) %>% 
  mutate(champion = case_when(year == 2021 ~ "VER",
                              year == 2020 ~ "HAM",
                              year == 2019 ~ "HAM",
                              year == 2018 ~ "HAM",
                              year == 2017 ~ "HAM",
                              year == 2016 ~ "ROS",
                              year == 2015 ~ "HAM",
                              year == 2014 ~ "HAM",
                              year == 2013 ~ "VET",
                              year == 2012 ~ "VET",
                              year == 2011 ~ "VET",
                              year == 2010 ~ "VET",
                              year == 2009 ~ "BUT",
                              year == 2008 ~ "HAM",
                              year == 2007 ~ "RAI",
                              year == 2006 ~ "ALO",
                              year == 2005 ~ "ALO",
                              year == 2004 ~ "MSC",
                              year == 2003 ~ "MSC",
                              year == 2002 ~ "MSC",
                              year == 2001 ~ "MSC",
                              year == 2000 ~ "MSC"),
         constructor_champ = case_when(year == 2021 ~ "Red Bull",
                              year == 2020 ~ "Mercedes",
                              year == 2019 ~ "Mercedes",
                              year == 2018 ~ "Mercedes",
                              year == 2017 ~ "Mercedes",
                              year == 2016 ~ "Mercedes",
                              year == 2015 ~ "Mercedes",
                              year == 2014 ~ "Mercedes",
                              year == 2013 ~ "Red Bull",
                              year == 2012 ~ "Red Bull",
                              year == 2011 ~ "Red Bull",
                              year == 2010 ~ "Red Bull",
                              year == 2009 ~ "Brawn",
                              year == 2008 ~ "McLaren",
                              year == 2007 ~ "Ferrari",
                              year == 2006 ~ "Renault",
                              year == 2005 ~ "Renault",
                              year == 2004 ~ "Ferrari",
                              year == 2003 ~ "Ferrari",
                              year == 2002 ~ "Ferrari",
                              year == 2001 ~ "Ferrari",
                              year == 2000 ~ "Ferrari"))

glimpse(f1)
map_chr(f1, class)
```

```{r ggplot, echo = FALSE, eval = TRUE}
f1 %>% 
  mutate(gp_name_sub = str_replace_all(gp_name, "Grand Prix", ""),
         engine_disp = recode(engine_disp, "V10" = "V10",
                              "V8 KERS" = "V8",
                              "V8" = "V8",
                              "V6" = "V6"),
         engine_disp = fct_relevel(engine_disp, "V6", after = Inf)) %>% 
  distinct(year, constructor_season_points, gp_name_sub, engine_disp, constructor_name, round) %>% 
  group_by(year, gp_name_sub, engine_disp, constructor_name, round) %>% 
  summarize(points = sum(constructor_season_points)) %>% 
  ungroup() %>% 
  mutate(cut_points = cut(points, breaks = 5)) %>% 
  # count(cut_points)
  filter(cut_points != "(-0.765,153]") %>% 
  drop_na(gp_name_sub, points, round) %>% 
  ggplot(aes(fct_reorder(gp_name_sub, round), points)) + 
  geom_point(aes(color = as.factor(constructor_name)), size = 3) + 
  facet_wrap(~engine_disp, scale = "free") +
  coord_flip() + 
  theme(legend.title = element_blank()) + 
  labs(x = "",
       y = "Total Constructor(Team) Points",
       title = "Total Number of Points For Each Constructor",
       caption = "Note: V10 Era = 2000-2005
       V8 = 2006-2008
       V8 + KERS (Kinetic Energy Recovery System) Era = 2009-2013
       V6 (Hybrid Turbo) Era = 2014-2021")

f1 %>% 
  mutate(gp_name_sub = str_replace_all(gp_name, "Grand Prix", ""),
         engine_disp = recode(engine_disp, "V10" = "V10",
                              "V8 KERS" = "V8",
                              "V8" = "V8",
                              "V6" = "V6"),
         engine_disp = fct_relevel(engine_disp, "V6", after = Inf)) %>% 
  distinct(year, constructor_season_points, gp_name_sub, engine_disp, constructor_name, round) %>% 
  group_by(year, gp_name_sub, engine_disp, constructor_name, round) %>% 
  summarize(points = sum(constructor_season_points)) %>% 
  ungroup() %>% 
  mutate(cut_points = cut(points, breaks = 5)) %>% 
  # count(cut_points)
  # filter(cut_points != "(-0.765,153]") %>% 
  filter((year < 2010 & points > 50) |
         (year >= 2010 & points > 200)) %>% 
  drop_na(gp_name_sub, points, round) %>% 
  ggplot(aes(fct_reorder(gp_name_sub, round), points)) + 
  geom_point(aes(color = as.factor(constructor_name)), size = 3) + 
  facet_wrap(~year, scale = "free") +
  coord_flip() + 
  theme(legend.title = element_blank()) + 
  labs(x = "",
       y = "Total Constructor(Team) Points",
       title = "Total Number of Points For Each Constructor",
       caption = "Note: V10 Era = 2000-2005
       V8 = 2006-2008
       V8 + KERS (Kinetic Energy Recovery System) Era = 2009-2013
       V6 (Hybrid Turbo) Era = 2014-2021")

f1 %>% 
  mutate(gp_name_sub = str_replace_all(gp_name, "Grand Prix", ""),
         engine_disp = recode(engine_disp, "V10" = "V10",
                              "V8 KERS" = "V8",
                              "V8" = "V8",
                              "V6" = "V6"),
         engine_disp = fct_relevel(engine_disp, "V6", after = Inf)) %>% 
  distinct(year, drive_season_points, gp_name_sub, engine_disp, driver_initial_id, round) %>% 
  group_by(year, gp_name_sub, engine_disp, driver_initial_id, round) %>% 
  summarize(points = sum(drive_season_points)) %>% 
  ungroup() %>% 
  mutate(cut_points = cut(points, breaks = 5)) %>% 
  # count(cut_points)
  filter(cut_points == "(330,413]" |
           cut_points == "(248,330]") %>% 
  drop_na(gp_name_sub, points, round) %>% 
  ggplot(aes(fct_reorder(gp_name_sub, round), points)) + 
  geom_point(aes(color = as.factor(driver_initial_id)), size = 3) + 
  facet_wrap(~engine_disp, scale = "free") +
  coord_flip() + 
  theme(legend.title = element_blank()) + 
  labs(x = "",
       y = "Total Constructor(Team) Points",
       title = "Total Number of Points For Each Constructor",
       caption = "Note: V10 Era = 2000-2005
       V8 = 2006-2008
       V8 + KERS (Kinetic Energy Recovery System) Era = 2009-2013
       V6 (Hybrid Turbo) Era = 2014-2021")

f1 %>% 
  mutate(gp_name_sub = str_replace_all(gp_name, "Grand Prix", ""),
         engine_disp = recode(engine_disp, "V10" = "V10",
                              "V8 KERS" = "V8",
                              "V8" = "V8",
                              "V6" = "V6"),
         engine_disp = fct_relevel(engine_disp, "V6", after = Inf)) %>% 
  distinct(year, drive_season_points, gp_name_sub, engine_disp, driver_initial_id, round) %>% 
  group_by(year, gp_name_sub, engine_disp, driver_initial_id, round) %>% 
  summarize(points = sum(drive_season_points)) %>% 
  ungroup() %>% 
  mutate(cut_points = cut(points, breaks = 5)) %>% 
  # count(cut_points)
  filter(cut_points == "(330,413]" |
           cut_points == "(248,330]") %>% 
  drop_na(gp_name_sub, points, round) %>% 
  ggplot(aes(fct_reorder(gp_name_sub, round), points)) + 
  geom_point(aes(color = as.factor(driver_initial_id)), size = 3) + 
  facet_wrap(~year, scale = "free") +
  coord_flip() + 
  theme(legend.title = element_blank()) + 
  labs(x = "",
       y = "Total Driver Points",
       title = "Total Number of Points For Each Constructor",
       caption = "Note: V10 Era = 2000-2005
       V8 = 2006-2008; 2009-2013
       V6 (Hybrid Turbo) Era = 2014-2021")

```

```{r}
world <- map_data("world")
```

```{r}
number1 <- f1 %>% 
  distinct(year, constructor_name, constructor_season_pos_text, long, lat) %>% 
  group_by(year, constructor_name) %>% 
  filter(constructor_season_pos_text == "1")

ggplot() +
  geom_polygon(data = world,
               aes(long, lat, group = group),
               fill = "gray70",
               alpha = .5) + 
  geom_point(data = number1,
             aes(long, lat, color = constructor_name), size = 3) +
  facet_wrap(~year) + 
  theme(legend.title = element_blank()) +
  coord_fixed(1.3)

library(gganimate)
constructor_win_plot <- ggplot() +
  geom_polygon(data = world,
               aes(long, lat, group = group),
               fill = "gray70",
               alpha = .5) + 
  geom_point(data = number1,
             aes(long, lat, color = constructor_name), size = 3) +
  transition_time(as.numeric(year)) +
  theme(legend.title = element_blank()) +
    labs(title = "Constructor Wins",
         subtitle = "Year: {frame_time")

animate(constructor_win_plot,
        renderer = gifski_renderer())
# anim_save("constructor_win_plot.gif")
```

```{r}
number1_driver <- f1 %>% 
  distinct(year, driver_initial_id, drive_season_pos_text, long, lat) %>% 
  group_by(year, driver_initial_id) %>% 
  filter(drive_season_pos_text == "1")

ggplot() +
  geom_polygon(data = world,
               aes(long, lat, group = group),
               fill = "gray70",
               alpha = .5) + 
  geom_point(data = number1_driver,
             aes(long, lat, color = driver_initial_id), size = 3) +
  facet_wrap(~year) + 
  theme(legend.title = element_blank())

ggplot() +
  geom_polygon(data = world,
               aes(long, lat, group = group),
               fill = "gray70",
               alpha = .5) + 
  geom_point(data = number1_driver,
             aes(long, lat, color = as.factor(year)), size = 3) +
  facet_wrap(~fct_reorder(driver_initial_id, year)) + 
  theme(legend.title = element_blank())
```

```{r descriptives}
hybrid <- f1 %>% 
  filter(engine_disp == "V6")

# write.csv(hybrid, "hybrid.csv")



# hybrid %>%
#   select_if(is.numeric) %>%
#   cat_map(~ggplot(data = hybrid, aes(.x)) +
#             geom_histogram(bins = 15,
#                            color = "white",
#                            fill = "dodgerblue") +
#             labs(x = glue::glue("{.x}")))

# hybrid %>% 
#   ggplot(aes(log(alt))) + 
#   geom_histogram(bins = 15,
#                            color = "white",
#                            fill = "dodgerblue")

glimpse(hybrid)

hybrid %>% 
  mutate() %>% 
  dplyr::select(-x1,)
```

Notes for myself here.

1. `alt` should probably be transformed
2. interaction between `long` and `lat`
3. create as factor for `status_id`, maybe even change the role to id
4. potential interaction between completed laps and circuit
5. `race_result_points` may want to be a transformed variable
6. Update role for `position_order` since it appears to be for ordering purposes (ID)
7. `grid` should be a factor
8. `result_id` should be a factor; update role to id
9. `quali_pos` should be factor
10. `driver_number` should be id
11. `qualify_id` may be id
12. `pit_dur_ms` should be numeric, maybe look into cleaning because zero
13. `pit_lap_number` should be factor
14. `stop_number` should be a factor
15. `lap_time_ms` should be numeric
16. `race_pos` should be factor
17. `drive_season_wins` should be factor
18. `drive_season_position` should be factor
19. `drive_season_points` numeric
20. `driver_id` may be id
21. `driver_standings_id` numeric
22. `curcuit_id` should be id
23. `round` should be either id or factor
24. `year` could be numeric or factor
25. 

```{r}
hybrid %>% 
  dplyr::select(-X1)

names(hybrid)
glimpse(hybrid)

inspectdf::inspect_na(hybrid) %>% 
  inspectdf::show_plot()
```

```{r modeling}




```

